---
theme-settings:
  theme: default
  barposition: top
  footer-left: "Coffee Sourcing Dashboard Survey"

survey-settings:
  show-previous: false
  use-cookies: false
  auto-scroll: false
  rate-survey: false
  system-language: en
  highlight-unanswered: true
  highlight-color: blue
  capture-metadata: true
  all-required: true
---

```{r}
library(surveydown)
```

```{r}
htmltools::tags$script(htmltools::HTML('
  (function() {
    var mouseBuffer = [];

    document.addEventListener("mousemove", function(e) {
      mouseBuffer.push({
        x: e.clientX,
        y: e.clientY,
        wx: window.innerWidth,
        wy: window.innerHeight,
        t: Date.now(),
        pg: (typeof Shiny !== "undefined" && Shiny.shinyapp &&
             Shiny.shinyapp.$inputValues &&
             Shiny.shinyapp.$inputValues["sd_current_page"]) || ""
      });
    });

    setInterval(function() {
      if (mouseBuffer.length > 0 &&
          typeof Shiny !== "undefined" && Shiny.setInputValue) {
        var toSend = mouseBuffer.splice(0);
        try {
          Shiny.setInputValue("mouse_track", { events: toSend }, { priority: "event" });
        } catch(e) {
          mouseBuffer = toSend.concat(mouseBuffer);
        }
      }
    }, 500);
  })();
'))
```

--- welcome

# Coffee Sourcing Dashboard Survey

Welcome! You are a buyer for a coffee importer. The dashboard shows data on
**342 coffee farms**: the altitude the farm sits at, its size in hectares, the
average age of its trees, how many kilograms it yields per hectare, and the
price per kilogram its coffee sold for at auction. Each farm grows one of three
arabica varietals.

Use the dashboard to explore the data, then answer the questions that follow.

```{r}
sd_next(label = "Start Survey")
```

--- practice

# Practice

This one is just to get familiar with the dashboard controls. It doesn't count.

```{r}
sd_question(
  id     = "practice_size_age",
  type   = "mc",
  label  = "Across all farms, how are farm size and tree age related?",
  option = c(
    "Positively related"             = "positive",
    "Negatively related"             = "negative",
    "No relation"                    = "no_relation",
    "Cannot determine from the data" = "cannot_determine"
  )
)
```

```{r}
sd_next(label = "Continue")
```

--- decision

# Question 1

```{r}
sd_question(
  id     = "q1_altitude",
  type   = "mc",
  label  = "Q1. A cooperative is buying land to plant a new coffee plot, and wants the coffee to sell for the highest possible price per kilogram. Based on the data, should they buy land at a higher or a lower altitude?",
  option = c(
    "Higher altitude"                      = "higher",
    "Lower altitude"                       = "lower",
    "Altitude doesn't affect price per kg" = "no_effect",
    "Cannot determine from the data"       = "cannot_determine"
  )
)
```

```{r}
sd_question(
  id     = "q1_confidence",
  type   = "slider",
  label  = "How confident are you in your answer to Q1?",
  option = seq(0, 10, 1)
)
```

```{r}
sd_question(
  id    = "q1_reasoning",
  type  = "textarea",
  label = "How did you arrive at that answer? Please briefly describe your reasoning."
)
```

```{r}
sd_next(label = "Continue")
```

--- questions

# Remaining questions

```{r}
sd_question(
  id     = "q2_size_altitude",
  type   = "mc",
  label  = "Q2. Among farms of the same size, which varietal tends to be grown at a higher altitude — Caturra or Typica?",
  option = c(
    "Caturra"                             = "caturra",
    "Typica"                              = "typica",
    "Both are grown at the same altitude" = "same",
    "Cannot determine from the data"      = "cannot_determine"
  )
)
```

```{r}
sd_question(
  id     = "q3_yield",
  type   = "mc",
  label  = "Q3. Which varietal has the highest average yield per hectare?",
  option = c(
    "Bourbon"      = "bourbon",
    "Caturra"      = "caturra",
    "Typica"       = "typica",
    "All the same" = "all_same"
  )
)
```

```{r}
sd_question(
  id     = "q4_altitude_varietal",
  type   = "mc",
  label  = "Q4. Which varietal is grown at the highest average altitude?",
  option = c(
    "Bourbon"      = "bourbon",
    "Caturra"      = "caturra",
    "Typica"       = "typica",
    "All the same" = "all_same"
  )
)
```

```{r}
sd_question(
  id     = "q5_yield_price",
  type   = "mc",
  label  = "Q5. How are yield per hectare and price per kilogram related?",
  option = c(
    "Positively related"             = "positive",
    "Negatively related"             = "negative",
    "No relation"                    = "no_relation",
    "Cannot determine from the data" = "cannot_determine"
  )
)
```

```{r}
sd_question(
  id     = "q_confidence_overall",
  type   = "slider",
  label  = "How confident are you in your answers to Q2 through Q5?",
  option = seq(0, 10, 1)
)
```

```{r}
sd_question(
  id     = "q_familiarity",
  type   = "mc",
  label  = "Before today, how familiar were you with coffee growing or coffee sourcing?",
  option = c(
    "Not at all familiar" = "none",
    "Slightly familiar"   = "slight",
    "Moderately familiar" = "moderate",
    "Very familiar"       = "very"
  )
)
```

--- end

## Thank you for completing the survey!

```{r}
sd_close()
```
